Prestige bias in cultural evolutionary dynamics

### 2023-11-12 ms/ms.tex
continue revision..

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Optimal success-bias weight}
% TODO edit the next sentence.
We ran simulations of the role-model choice process during a single generation in which every copier evaluates its own optimal success-bias weight, $\alpha^*$, which minimizes the expected squared error between the chosen trait value and the optimal trait value $\hat{A}$,
\begin{equation}\label{eq:optimal_alpha}
\alpha^* = \emph{argmin} \sum_{j=1}^N\frac{\alpha A_j + (1-\alpha) K_j}{\sum_{l=1}^N\alpha A_l + (1-\alpha) K_l} (\hat{A}-A_j)^2 \;,
\end{equation}
where $A_j$ is the trait of role-model $j$ and $K_j$ the number of copiers that already chose role-model~$j$.
Simply put, each copier estimates what success-bias weight $\alpha^*$ will result in copying a trait that is most similar to the ideal trait value $\hat{A}$.
Indeed, if the trait value is correlated with fitness, the optimal success-bias weight would increase the fitness of individuals. However, here we ignore the effects of natural selection, focusing instead on selectively neutral traits.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Optimal success-bias weight}
% TODO edit the next sentence -- mention this is in the continous trait model
In the above, we assumed that $\alpha$ is homogeneous in the population. 
Next
We ran simulations of the role-model choice process during a single generation in which every copier evaluates its own optimal success-bias weight, $\alpha^*$, which minimizes the expected squared error between the chosen trait value and the optimal trait value $\hat{A}$,
\begin{equation}\label{eq:optimal_alpha}
\alpha^* = \emph{argmin} \sum_{j=1}^N\frac{\alpha A_j + (1-\alpha) K_j}{\sum_{l=1}^N\alpha A_l + (1-\alpha) K_l} (\hat{A}-A_j)^2 \;,
\end{equation}
where $A_j$ is the trait of role-model $j$ and $K_j$ the number of copiers that already chose role-model~$j$.
Simply put, each copier estimates what success-bias weight $\alpha^*$ will result in copying a trait that is most similar to the ideal trait value $\hat{A}$.
Indeed, if the trait value is correlated with fitness, the optimal success-bias weight would increase the fitness of individuals. However, here we ignore the effects of natural selection, focusing instead on selectively neutral traits.
